Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-04 doc/PRF2022/PRF_main.tex
added figures

Channel Flow: 
\begin{enumerate}
\item Convergence tests for $N_b=25$ vesicle in a narrow channel.  Add energy profile.

@@

>>>>

{\bf May do list:}
Channel Flow: 
\begin{enumerate}
\item Convergence tests for $N_b=25$ vesicle in a narrow channel.  Add energy profile.

@@

{\bf More results:}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{multilamellar_shear_Energy}
    \includegraphics[width=0.4\textwidth]{multilamellar_shear_MSD}
  \end{center}
      \caption{A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$. We compute the energy and the mean square displacement $MSD(t) = \frac{1}{N_b^2}\sum_{i=1}^{N_b} ||D(t)-D(0) ||_2$ where the matrix $D$ is the pairwise distance matrix at time $t$.    }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{multilamellar_shear0p1_Energy_LsFs}
    \includegraphics[width=0.4\textwidth]{multilamellar_shear0p1_MSD_LsFs}
  \end{center}
    \caption{ A multi-lamellar structure in a shear flow when the shear rate is $\dot\gamma=0.1$. We tune the length scale parameters, radius, $\rho$ and $\rho_0$, by $\pm 5\%$ and the force scale parameters, $\gamma$ and $M$, by $\pm 5\%$.    }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{multilamellar_TG_Energy}
    \includegraphics[width=0.4\textwidth]{multilamellar_TG_MSD}
  \end{center}
    \caption{A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{checker_board_shear_Energy}
    \includegraphics[width=0.4\textwidth]{checker_board_shear_MSD}\\
  \includegraphics[width=0.4\textwidth]{checker_board_shear0p125_OP}
    \includegraphics[width=0.4\textwidth]{checker_board_shear0p15_OP}
  \end{center}
\caption{A checker board in shear flows with shear rates $\dot\gamma=\{0.125, 0.15\}$. We propose the order parameter defined by $S_2 = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{checker_board_TG_Energy}
    \includegraphics[width=0.4\textwidth]{checker_board_TG_MSD}\\
      \includegraphics[width=0.4\textwidth]{checker_board_TG0p2_OP}
    \includegraphics[width=0.4\textwidth]{checker_board_TG0p3_OP}
  \end{center}
\caption{A checker board in Taylor-Green flows when the flow strength $V_0=\{0.2,0.3\}$. }
\end{figure}
